The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-03 writing/manuscript.Rmd
parameter changes in text table

$$
z = n_{homo} + d * n_{het}
$$
where $n_{homo}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci. A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.

@@

| Default Parameters               |           |
|----------------------------------|-----------|
| Crossover probability            | 0.05      |
| Mutation probability             | $10^{-4}$ |
| Population size                  | 500       |
| Number of loci                   | 100       |
| Exponent of the fitness function | 1         |
| Dominance                        | 0.5       |
| Years                            | 100       |
| Generations per year             | 20        |
| Seasonal balance                 | 2         |

@@

```{r, fig.width = 10}
# Small fig.width
knitr::include_graphics("G10.png")
knitr::include_graphics("G50.png")
```

>>>>

$$
z = n_{hom} + d * n_{het}
$$
where $n_{hom}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci. A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.

@@

| Default Parameters               |           |
|----------------------------------|-----------|
| Crossover probability            | 0.05      |
| Mutation probability             | $10^{-4}$ |
| Population size                  | 500       |
| Number of loci                   | 100       |
| Exponent of the fitness function | 1         |
| Dominance                        | 0.5       |
| Years                            | 300       |
| Generations per year             | 20        |
| Seasonal balance                 | 2         |

@@

# ```{r, fig.width = 10}
# # Small fig.width
# knitr::include_graphics("G10.png")
# knitr::include_graphics("G50.png")
# ```
